\section{Summary}

Based on all the analysis above, our observations can be summarized as the following themes.

\subsubsection{Majority of GitHub users don't use public Gists.}

For those GitHub users we randomly sampled, only 5.82\% of them have at least one public Gist. For those who have public Gists, half of them have less than 5 Gists. Also, 86.79\% of those sampled Gists only contain 1 file. All these results show that GitHub users generally don't use public Gists much. 

\subsubsection{Gists usually contain small files.}

According to the metadata provided by GitHub, we found that majority of Gist files were around 1KB. The median size was 714 Bytes. As for all the text files, 87.1\% of them have less than 100 lines, and the median number of lines is 23. We also calculated the source lines of code for all the source files, and todo of them have less than todo lines with median as todo lines. 

\subsubsection{Gists content shows a great variety.}

There are 113 MIME types and 257 programming languages discovered from all the Gist files we sampled. Although majority of Gist files are source files, we also observed data files (such as JSON, CSV, XML) and binary files (such as images, audios and even videos) in Gists. During our manual inspection against Gists content, we also found blogs, letters, and even restaurant menus. 

\subsubsection{Users don't collaborate on Gists.}
We found Gists are mostly personal artifacts. Among all of the sampled Gists, 62.9\% of them had a single commit (by the owner obviously), and only 1.85\% had more than 10 commits. The creation and the latest update of 83.7\% of Gists happened at the same day. 94.6\% of Gists have never been forked by other users, and only 7.3\% of Gists have been commented once or more. 

\subsubsection{Gists are being used for a variety of purposes.}
Based on our searched results from Websites and Twitter, a great variety was discovered in terms of what people use Gists for: some people use it to create components that can be embedded in their blogs; some use it to keep track of some activities by a version controlled list; some save their notes such as learning outcomes in Gists; some share content with others simply by Gist URLs; some use it to draft their writings.