\newpage
\TOCadd{Abstract}

\noindent \textbf{Supervisory Committee}
\tpbreak
\panel

\begin{center}
\textbf{ABSTRACT}
\end{center}

GitHub is a popular source code hosting site which serves as not only a collaborative coding platform but also a social network. Various unique features of GitHub have greatly facilitated developers' collaboration, communication, and coordination, which has given rise to many research in different angles. One of GitHub features is Gists, which is expected to be a tool for instantly sharing code, notes, and snippets. However, it hasn't been paid much attention by researchers. 

In this study, with the goal of understanding what GitHub Gists look like and how they are used, both quantitative and qualitative analyses were performed which was composed of three parts. The first part was a quantitative analysis against the metadata of 562,993 GitHub users, 618,393 Gists and 793,891 files contained in those Gists. For the second part, manual coding was conducted for the content of 400 randomly selected Gists. The third part was qualitative analysis against the searched results from Google and Twitter about users' description of how they use Gists. 

The study result shows that only a small portion of GitHub users use Gists. Most of Gists contain small snippets of source code, but a great variety of Gists content was also discovered. Majority of Gists were not updated frequently, and users rarely fork or comment other users' Gists. Gists are being used in lots of ways, from saving snippets of code or notes, sharing files, to drafting their writings.