\startchapter{Conclusion}
In this study, with the goal of understanding what GitHub gists look like and how they are used, we performed quantitative analysis against 618k Gists and 562k GitHub user, manual coding for the content of 400 randomly selected Gists, and manual analysis against the searched results from Google and Twitter about users' description of how they use Gists. 

Our results can be summarized as follows:

\textsl{What do Gists look like?} Only a small portion of GitHub users use Gists. Gists usually contain small snippets of source code, but a wide variety of Gists content was also discovered including data files (such as JSON, XML), binary files (such as images, audios, vidoes), and text files of various kinds (such as blogs, logs, letters, restaurant menus). Majority of Gists were not updated frequently, and users rarely fork or comment other users' Gists.

\textsl{How are Gists being used?} Although GitHub expects users to use Gists to instantly share code snippets, people are actually using Gists for various purposes: some people use it to create components that can be embedded in their blogs; some use it to keep track of some activities by a version controlled list; some save their notes such as learning outcomes in Gists; some share content with others simply by Gist URLs; some use it to draft their writings.

Gists can serve for lots of purposes by taking advantage of either its convenient editor or version control support. We hope it will become more and more popular in the future..